Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-14 paper/paper.tex

\begin{table}
  %\vspace{-4ex}
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  %\small
  \begin{tabular}{rr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc & \percentSuiteTestJSC{}\\
    \veight{} & \percentSuiteTestVeight{} \\
    \chakra{} & \percentSuiteTestChakra{} \\
    \smonkey{} & \percentSuiteTestSM{} \\
    \hermes & \percentSuiteTestHermes{} \\
    \bottomrule
  \end{tabular}
  %\normalsize
\end{table}

@@

Results show that there are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc, \veight, and \smonkey
%, whereas \chakra performs
%worse when compared to the other engines.
%\Fix{This happens because \hermes
%still has many unsupported features, such as Proxy, Promisse, and Async.}
Moreover, one can also note that \chakra has a low passing ratio
in this test suite. Interestingly, it is also the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. As discussed above,
it is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs.

@@

\Mar{moved from Section 4. check if useful. $\rightarrow$}
\Fix{It is worth noting that we also
  did not include the tests from \hermes\ in the table because, as the
  reader shall see in Table~\ref{tab:test262}, \hermes presents a very
  low adherence to the Test262 conformance suite. If we decided to
  keep \hermes, considering only the number of passing tests in all
  engines (the ``no-fail-in-all'' column), it would significantly
  reduce our amount of test files.}  $\leftarrow$\Breno{Haven't we
  decided that Hermes should be removed from Table 3?  If yes, maybe
  this explanation will only create confusing.}  \Mar{Not sure if I
  understood the conclusion. Do you mean the total amount of test
  (also from other suites)? Why?}

@@

%-----Issue \#35, Table~\ref{tab:test-transplantation-bugs}
\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:test-transplantation-bugs}.} We
reported the snippet \CodeIn{"use strict" 010} to the
\textbf{\smonkey} development team as a bug and the bug was confirmed
in a few hours.  This is a test case originally from the \hermes suite
using test transplantation.  According the specification, in strict
mode, the engine must use the prefix '0o' or '0O' to represent octal
numeric literals. This is an issue that explores a deprecated octal
token after ASI (Automatic Semicolon Insertion). The other engines
throw a SyntaxError due to the missing of the octal token, but \smonkey
returns an integer \CodeIn{8} that represents \CodeIn{010} in octal.

@@

%-----Issue \#24, Table~\ref{tab:bugs}
\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet
\CodeIn{b+/v/a} represents a bug confirmed in \textbf{\hermes} engine with
differential testing using radamsa.
The original test case contains a string concatenation.
This is a case of validation of RegEx flags. The fuzzer mutates
the file with a regular expression \CodeIn{/v/} after the plus operator.
In this case, the plus operator turns into a flag of the RegEx \CodeIn{+/v/},
but this flag is not valid. The expected behavior is to throw an early
SyntaxError due to the invalid regular expression flag,
but \hermes\ seems not to treat the early validation of the regexp flags
as explained by one of their developers.

>>>>

\begin{table}
  %\vspace{-4ex}
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  %\small
  \begin{tabular}{rr}
    \toprule
    engine & \% passing \\
    \midrule
    \veight{} & \percentSuiteTestVeight{} \\
    \smonkey{} & \percentSuiteTestSM{} \\
    \jsc & \percentSuiteTestJSC{}\\
    \chakra{} & \percentSuiteTestChakra{} \\
    \hermes & \percentSuiteTestHermes{} \\
    \bottomrule
  \end{tabular}
  %\normalsize
\end{table}

@@

Results show that there are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc, \veight, and \smonkey
%, whereas \chakra performs
%worse when compared to the other engines.
%\Fix{This happens because \hermes
%still has many unsupported features, such as Proxy, Promisse, and Async.}
Moreover, one can also note that \hermes and \chakra have a low passing ratio
in this test suite. Interestingly, \chakra is also the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. As discussed above,
it is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs. Finally, since \hermes has a
very low adherence to the Test262 conformance suite, we opted to conduct
a case study with them. Therefore, we will only discuss \hermes data at
Section~\ref{sec:hermes}.

@@

%\Mar{moved from Section 4. check if useful. $\rightarrow$}
%\Fix{It is worth noting that we also
%  did not include the tests from \hermes\ in the table because, as the
%  reader shall see in Table~\ref{tab:test262}, \hermes presents a very
%  low adherence to the Test262 conformance suite. If we decided to
%  keep \hermes, considering only the number of passing tests in all
%  engines (the ``no-fail-in-all'' column), it would significantly
%  reduce our amount of test files.}  $\leftarrow$\Breno{Haven't we
%  decided that Hermes should be removed from Table 3?  If yes, maybe
%  this explanation will only create confusing.}  \Mar{Not sure if I
%  understood the conclusion. Do you mean the total amount of test
%  (also from other suites)? Why?}

@@

%-----Issue \#35, Table~\ref{tab:test-transplantation-bugs}
\vspace{1ex}\noindent\textbf{Issue \#32, Table~\ref{tab:test-transplantation-bugs}.} We
reported the snippet \CodeIn{"use strict" 010} to the
\textbf{\smonkey} development team as a bug and the bug was confirmed
in a few hours.  This is a test case originally from the \hermes suite
using test transplantation.  According the specification, in strict
mode, the engine must use the prefix '0o' or '0O' to represent octal
numeric literals. This is an issue that explores a deprecated octal
token after ASI (Automatic Semicolon Insertion). The other engines
throw a SyntaxError due to the missing of the octal token, but \smonkey
returns an integer \CodeIn{8} that represents \CodeIn{010} in octal.

@@

%-----Issue \#24, Table~\ref{tab:bugs}
\vspace{1ex}\noindent\textbf{Bug reported on \hermes.} The snippet
\CodeIn{b+/v/a} represents a bug confirmed in \textbf{\hermes} engine with
differential testing using radamsa.
The original test case contains a string concatenation.
This is a case of validation of RegEx flags. The fuzzer mutates
the file with a regular expression \CodeIn{/v/} after the plus operator.
In this case, the plus operator turns into a flag of the RegEx \CodeIn{+/v/},
but this flag is not valid. The expected behavior is to throw an early
SyntaxError due to the invalid regular expression flag,
but \hermes\ seems not to treat the early validation of the regexp flags
as explained by one of their developers.
